### 2012-05-30 docs/getting_started/getting_started.tex
no longer need to copy in the helm_table.dat

\item {\em Copy in auxillary files}.

This problem uses the {\tt helmeos} equation of state, so 
we need to copy in the data table for the equation of state, {\tt
  extern/EOS/helmeos/helm\_table.dat}.

\begin{verbatim}
cp ../../../extern/EOS/helmeos/helm_table.dat .
\end{verbatim}

>>>>

Note, at the end of the build process, a link will be made in the current
directory to the data
table needed for the equation of state ({\tt extern/EOS/helmeos/helm\_table.dat}).
